Feasibility of a Cluster Randomised Trial on the Effect of Trauma Life Support Training: A Pilot Study

### 2025-01-08 cover-letter.qmd
Restore directory state to BMJ Open version

I am submitting our manuscript, “Feasibility of a Cluster Randomised Trial on the Effect of Trauma Life Support Training: A Pilot Study” for consideration for publication in the British Journal of Surgery.

This study evaluates the feasibility of conducting a full-scale trial to assess the impact of trauma life support training programs on patient outcomes. The findings include consent rates, data quality, and effect size estimates, which are essential for planning a future full-scale trial. We believe this work addresses an important gap in evidence for trauma care and will be of interest to your readers.

>>>>

I am submitting our manuscript, “Feasibility of a Cluster Randomised Trial on the Effect of Trauma Life Support Training: A Pilot Study” for consideration for publication in JAMA Surgery.

This study evaluates the feasibility of conducting a full-scale trial to assess the impact of trauma life support training programs on patient outcomes. The findings include consent rates, data quality, and effect size estimates, which are essential for planning future research. We believe this work addresses an important gap in evidence for trauma care and will be of interest to your readers.

### 2025-01-08 manuscript.Rmd
Restore directory state to BMJ Open version

##### Li Felländer-Tsai, MD, PhD (LFT) `r insert_orcid_link("0000-0003-0693-6080")` <!-- Accepted, li.tsai@ki.se -->
Division of Orthopaedics and Biotechnology, Department of Clinical Science Intervention and Technology (CLINTEC), Karolinska Institutet, Stockholm, Sweden.

@@

##### Anurag Mishra (AM) <!-- Accepted -->
Department of Surgery, Maulana Azad Medical College, New Delhi, India.

>>>>

##### Li Felländer-Tsai, MD, PhD (LFT) `r insert_orcid_link("0000-0003-0693-6080")` <!-- Accepted -->
Division of Orthopaedics and Biotechnology, Department of Clinical Science Intervention and Technology (CLINTEC), Karolinska Institutet, Stockholm, Sweden.

@@

##### Anurag Mishra (AM)
Department of Surgery, Maulana Azad Medical College, New Delhi, India.
